Manuscript

### 2018-10-30 manuscript.Rmd
start CCLE overlap analysis

```{r}
library(bsselectR)
install.packages("cowplot")
library(data.table)
library(ggpubr)
library(ggsignif)
library(grid)
library(gridExtra)
library(kableExtra)
library(reshape2)
library(tidyverse)
```

@@

@@

@@

gdsc_druggene_mad_summ <- gdsc_data_ptmuts %>% group_by(Drug_Gene, Mutation_Status_Nonsilent) %>% summarize(Mean_AUC = mean(AUC))
gdsc_druggene_mad_summ <- dcast(gdsc_druggene_mad_summ, Drug_Gene ~ Mutation_Status_Nonsilent)
gdsc_druggene_mad_summ$MAD <- abs(gdsc_druggene_mad_summ$Mutant - gdsc_druggene_mad_summ$Other)
gdsc_druggene_p_summ <- gdsc_signif_g2p_ByDrug_all
gdsc_druggene_p_summ$Drug_Gene <- paste0(gdsc_druggene_p_summ$Drug, "_", gdsc_druggene_p_summ$Hugo_Symbol)
gdsc_druggene_summ <- merge(merge(g2p_druggene_p_tally, gdsc_druggene_p_summ[, c("Drug_Gene", "p")], by = "Drug_Gene", all.y = TRUE), gdsc_druggene_mad_summ, by = "Drug_Gene", all = TRUE)
gdsc_druggene_summ$n <- ifelse(is.na(gdsc_druggene_summ$n), 0, gdsc_druggene_summ$n)
gdsc_druggene_summ$InG2P <- ifelse(gdsc_druggene_summ$n != 0, "Yes", "No")
gdsc_druggene_summ$Dataset <- "GDSC"
gdsc_p_ttest <- t.test(gdsc_druggene_summ$p ~ gdsc_druggene_summ$InG2P)
gdsc_p_ttest_res <- paste0("t = ", round(gdsc_p_ttest$statistic, 3), ", df = ", round(gdsc_p_ttest$parameter, 3), ", p = ", round(gdsc_p_ttest$p.value, 3))
gdsc_mad_ttest <- t.test(gdsc_druggene_summ$MAD ~ gdsc_druggene_summ$InG2P)
gdsc_mad_ttest_res <- paste0("t = ", round(gdsc_mad_ttest$statistic, 3), ", df = ", round(gdsc_mad_ttest$parameter, 3), ", p = ", round(gdsc_mad_ttest$p.value, 3))
```

```{r, eval=FALSE, include=FALSE}
plot_mad_ccle_a <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(color = InG2P, x = MAD, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = c(0.75, 4, 0.2), y = 110, label = Test_Results_MAD)) +
  labs(x = "Gene-drug association difference in mean AUC between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
  theme(legend.position = "top")

plot_p_a <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(color = InG2P, x = p, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
  labs(x = "Gene-drug association p-value by mutation status", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
  theme(legend.position = "top")
```

```{r}
g2p_druggene_all_summ <- rbind(ccle_druggene_summ, ctrp_druggene_summ, gdsc_druggene_summ)
g2p_druggene_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), 
                                         Test_Results_p = c(ccle_p_ttest_res, ctrp_p_ttest_res, gdsc_p_ttest_res),
                                         Test_Results_MAD = c(ccle_mad_ttest_res, ctrp_mad_ttest_res, gdsc_mad_ttest_res))
```

@@

## P-value
plot_p_point <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(color = InG2P, x = p, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
  labs(x = "Gene-drug association difference in mean AUC between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

@@

>>>>

```{r}
library(bsselectR)
library(data.table)
library(ggpubr)
library(ggsignif)
library(kableExtra)
library(reshape2)
library(tidyverse)
```

@@

## CRISPR: Mutation status counts

@@

## Drugscreen G2P evidence

@@

gdsc_druggene_mad_summ <- gdsc_data_ptmuts %>% group_by(Drug_Gene, Mutation_Status_Nonsilent) %>% summarize(Mean_AUC = mean(AUC))
gdsc_druggene_mad_summ <- dcast(gdsc_druggene_mad_summ, Drug_Gene ~ Mutation_Status_Nonsilent)
gdsc_druggene_mad_summ$MAD <- abs(gdsc_druggene_mad_summ$Mutant - gdsc_druggene_mad_summ$Other)
gdsc_druggene_p_summ <- gdsc_signif_g2p_ByDrug_all
gdsc_druggene_p_summ$Drug_Gene <- paste0(gdsc_druggene_p_summ$Drug, "_", gdsc_druggene_p_summ$Hugo_Symbol)
gdsc_druggene_summ <- merge(merge(g2p_druggene_p_tally, gdsc_druggene_p_summ[, c("Drug_Gene", "p")], by = "Drug_Gene", all.y = TRUE), gdsc_druggene_mad_summ, by = "Drug_Gene", all = TRUE)
gdsc_druggene_summ$n <- ifelse(is.na(gdsc_druggene_summ$n), 0, gdsc_druggene_summ$n)
gdsc_druggene_summ$InG2P <- ifelse(gdsc_druggene_summ$n != 0, "Yes", "No")
gdsc_druggene_summ$Dataset <- "GDSC"
gdsc_p_ttest <- t.test(gdsc_druggene_summ$p ~ gdsc_druggene_summ$InG2P)
gdsc_p_ttest_res <- paste0("t = ", round(gdsc_p_ttest$statistic, 3), ", df = ", round(gdsc_p_ttest$parameter, 3), ", p = ", round(gdsc_p_ttest$p.value, 3))
gdsc_mad_ttest <- t.test(gdsc_druggene_summ$MAD ~ gdsc_druggene_summ$InG2P)
gdsc_mad_ttest_res <- paste0("t = ", round(gdsc_mad_ttest$statistic, 3), ", df = ", round(gdsc_mad_ttest$parameter, 3), ", p = ", round(gdsc_mad_ttest$p.value, 3))

g2p_druggene_all_summ <- rbind(ccle_druggene_summ, ctrp_druggene_summ, gdsc_druggene_summ)
g2p_druggene_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), 
                                         Test_Results_p = c(ccle_p_ttest_res, ctrp_p_ttest_res, gdsc_p_ttest_res),
                                         Test_Results_MAD = c(ccle_mad_ttest_res, ctrp_mad_ttest_res, gdsc_mad_ttest_res))
```

@@

## P-value
plot_p_point <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(color = InG2P, x = p, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

@@

```{r}
crispr_ccl <- unique(select(crispr_data, Broad_ID, CCLE_Name))
ccle_ccl <- unique(select(ccle_data, Broad_ID, CCLE_Name, accession_id))
ctrp_ccl <- unique(select(ctrp_data, Broad_ID, CCLE_Name, accession_id))
gdsc_ccl <- unique(select(gdsc_data, Broad_ID, CCLE_Name, accession_id))

# all_ccl <- merge(ccle_ccl, ctrp_ccl, by = c("Broad_ID", "CCLE_Name", "accession_id"), all = TRUE)
```
